### 2020-03-03 draft_ABP.tex
update;

As shown in the last subsection, the $n$-dimensional permutahedron is associated 
with the set of all non-empty subsets of $[0,n]$, which is denoted by $\mathscr P_n$. 
The number of facets of $\mathscr P_n$ is $2^n-2$.

(equations of facets?)

ABHY conditions:
\bea
C_I = (-1)^{|I|} \left( \sum_{i \in I} X_i - \sum _{{i<j}\atop{i,j \in I}} X_{ij} +\cdots + (-1)^{|I|+1}  X_I \right) \nonumber
\eea
for all non-empty subsets $I \subset \{0,1,\cdots,n\}$ with the understanding that $C_{I} =0$ for all singlets $I$ and $X_{I} =0$ for $I=\{ 0,1,\cdots,n \}$.

(proof?)

Then we can then solve for the corresponding $u's$ :
\bea
u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber \\
u^{'}_J &=& \prod_{{0 \in I}\atop{ \{0,\cdots,n\} - I \subset J}} x_I^{(-1)^{|I|-|J|+\color{red}{mod(n, 2)}}} \nonumber
\eea

>>>>

As shown in the last subsection, the $n$-dimensional permutahedron is associated 
with the set of all non-empty subsets of $[0,n]$, which is denoted by $\mathscr P_n$. 
Each facet of $P_n$ is lebeled by a non-empty proper subset $I$ of $[0,n]$, whose
equation is 
\begin{equation}
	F_J:=\sum_{J\neq \varnothing, J\subset I} S_J=0,
\end{equation}
so the number of facets of $\mathscr P_n$ is $2^n-2$. The AHBY condition 
can be solved from above equations:
\[
	S_I = (-1)^{|I|+1}\sum_{i\in I} S_i,
\]
for all non-empty subsets $I \subset [0,n]$ which are not singlets.

(proof of equations fo facets or ABHY condition?)

To get $u$-equations, we should solve $S_J$ by $F_J$ for eq.(\theequation), the 
solution is 
\[
	S_I=\sum_{J\neq \varnothing,J\subset I} (-1)^{|J|-|I|}F_J,
\]
then
\[
	\prod_{I\neq \varnothing,I\subset [0,n]}u_I^{F_I}=
	\prod_{I\neq \varnothing,I\subset [0,n]}x_I^{S_I}=
	\prod_{\varnothing\neq J\subset I\subset [0,n]}
	x_I^{(-1)^{|J|-|I|}F_J}=
	\prod_{J\neq \varnothing,J\subset [0,n]}
	\prod_{I\supset J}(x_I^{(-1)^{|J|-|I|}})^{F_J}
\]
gives that
\[
	u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}
\]
